Symmetric Peer-to-Peer Applications

### 2022-10-28 p2p-22.tex
...

\documentclass[10pt,journal,compsoc]{IEEEtran}

@@

\title{
    Symmetric Peer-to-Peer Applications
}

\author{
    Francisco Sant'Anna~\IEEEmembership{Department of Computer Science, Rio de Janeiro State University}
}

\IEEEtitleabstractindextext{%
\begin{abstract}
In real-time networked applications, such as shared documents, users can
interact remotely and yet share the exact same experience as if they were in a
single machine.
%
In this work, we propose a middleware for \emph{symmetric peer-to-peer
applications} in which decentralized instances can broadcast asynchronous
events and yet conform to identical behavior.
%
Peers are allowed to join and leave the network at any time.
Application developers must adhere to a restricted API, which is deterministic,
stateless, and only supports pre-allocated memory.
%
The middleware is responsible for synchronizing the events in a global shared
timeline across the network.
Also, based on memory snapshots and deterministic simulation, a ``time machine''
can rollback conflicting peers to resynchronize their state.
%
We show that the middleware can handle applications with over 20 peers in a
heterogeneous topology under high churn.
For instance, in a simulation scenario of 25 events per minute with a network
latency of $50ms$, the peers need to roll back and resynchronize only $3\%$ of
the time.
\end{abstract}

\begin{IEEEkeywords}
collaboration, determinism, peer-to-peer, time machine
\end{IEEEkeywords}}

@@

% TOTAL: 12 pages

@@

\IEEEPARstart{R}{eal-time} networked applications allow multiple users to
interact remotely and yet share the same experience.
Examples of these \emph{symmetric distributed applications}~\cite{gals} are
shared documents, watch parties, and multi-player games.
%
In order to reproduce the exact behavior in multiple devices, the application
must be able to synchronize time and execution across the network.
In addition, since users can interact asynchronously with the application,
event occurrences must somehow be synchronized back across devices.

@@

% docs.google.com/spreadsheets/d/1CpMmEgabJq2XQeTDW_BNCV4JWrcMlELuaEjDtw7kwg0/
\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{table}
  \caption{
    Related work regarding
        (a) how the network is organized,
        (b) how global time is determined, and
        (c) how events are propagated and applied.
    \label{fig.table}
  }
\end{figure}

\begin{figure*}[p]
  \centering
  \includegraphics[width=\linewidth]{algos}
  \caption{
    \label{fig.algos}
    Four approaches to symmetric distributed applications: Croquet, GALS,
    CRDTs, and this work.
    The vertical arrows in parallel represent the timelines in nodes in the
    network.
    The arrows crossing nodes represent communication between them.
  }
\end{figure*}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{move}
    \caption[XXX] {
        A moving rectangle is controlled by peers connected indirectly.
        Users can press \code{↑ ↓ → ←} to change the direction of the
        rectangle or \code{SPACE} to pause the application.
        The inputs are applied simultaneously in all peers, as if they were
        mirrors of a single application.
        Video: \url{http://youtube.com/TODO}
        \label{fig.move}
    }
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{middleware}
  \caption{
    Applications generate asynchronous events and communicate through an API
    with the middleware.
    The middleware orchestrates the peers, synchronizing their ticks locally
    and broadcasting events with a $\Delta$ delay.
    \label{fig.middleware}
  }
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=\linewidth]{topo}
  \caption{
    \label{fig.topo}
    Network topology: 21 peers organized as a straight line ($0-3$), a simple
    cycle ($3-8$), a second straight line ($8-11$), a full connected cycle
    ($12-17$), and a third straight line ($17-20$).
    %An optional link ($0,20$) creates a long cycle in the network.
  }
\end{figure*}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=2in]{mult}
  \caption{
    \label{fig.mult}
Event delays in $ms$ considering the network latency, delay multiplier, and the
average of 5 hops between peers from Figure~\ref{fig.topo}.
    }
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=\linewidth]{baks}
  \caption{
    \label{fig.baks}
The $5x$, $2x$, and $x$ delay regions each contains $36$ measures for multiple
configurations of event rate ($5-200~evt/min$ and network latency ($5-500ms$).
%
The color thresholds (\emph{white}, \emph{yellow}, \emph{red}, \emph{black})
are arbitrary but help to distinguish between regions of interest.
%
The experiments uses $1$ process for each peer in a single Linux machine
(\emph{i7/16GB}).
    }
\end{figure*}

@@

\bibliographystyle{IEEEtran}
\bibliography{tpd-22}

\begin{comment}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{chico}}]{Francisco Sant'Anna}
received his PhD degree in Computer Science from PUC-Rio, Brazil in
2013.
In 2016, he joined the Faculty of Computer Science at the Rio de Janeiro State
University, Brazil.
His research interests include Programming Languages and Concurrent \&
Distributed Systems.
\end{IEEEbiography}
\end{comment}

>>>>

\documentclass[sn-mathphys,iicol]{sn-jnl}% Math and Physical Sciences Reference Style 
%\documentclass[default,iicol]{sn-jnl}% Default with double column layout

\jyear{2022}%

\raggedbottom
%%\unnumbered% uncomment this for unnumbered level heads

@@

\title[Article Title]{
    Symmetric Peer-to-Peer Applications
}

\author{\fnm{Francisco} \sur{Sant'Anna} \email{francisco@ime.uerj.br}}
\affil{\orgdiv{Department of Computer Science}, \orgname{Rio de Janeiro State University}, \orgaddress{\country{Brazil}}}

\abstract{
In real-time networked applications, such as shared documents, users can
interact remotely and yet share the exact same experience as if they were in a
single machine.
%
In this work, we propose a middleware for \emph{symmetric peer-to-peer
applications} in which decentralized instances can broadcast asynchronous
events and yet conform to identical behavior.
%
Peers are allowed to join and leave the network at any time.
Application developers must adhere to a restricted API, which is deterministic,
stateless, and only supports pre-allocated memory.
%
The middleware is responsible for synchronizing the events in a global shared
timeline across the network.
Also, based on memory snapshots and deterministic simulation, a ``time machine''
can rollback conflicting peers to resynchronize their state.
%
We show that the middleware can handle applications with over 20 peers in a
heterogeneous topology under high churn.
For instance, in a simulation scenario of 25 events per minute with a network
latency of $50ms$, the peers need to roll back and resynchronize only $3\%$ of
the time.
}

\keywords{
collaboration, determinism, peer-to-peer, time machine
}

%%\pacs[JEL Classification]{D8, H51}

%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}

@@

@@

Real-time networked applications allow multiple users to interact remotely and
yet share the same experience.
Examples of these \emph{symmetric distributed applications}~\cite{gals} are
shared documents, watch parties, and multi-player games.
%
In order to reproduce the exact behavior in multiple devices, the application
must be able to synchronize time and execution across the network.
In addition, since users can interact asynchronously with the application,
event occurrences must somehow be synchronized back across devices.

@@

% docs.google.com/spreadsheets/d/1CpMmEgabJq2XQeTDW_BNCV4JWrcMlELuaEjDtw7kwg0/
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{table}
  \caption{
    Related work regarding
        (a) how the network is organized,
        (b) how global time is determined, and
        (c) how events are propagated and applied.
    \label{fig.table}
  }
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{algos}
  \caption{
    \label{fig.algos}
    Four approaches to symmetric distributed applications: Croquet, GALS,
    CRDTs, and this work.
    The vertical arrows in parallel represent the timelines in nodes in the
    network.
    The arrows crossing nodes represent communication between them.
  }
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{move}
    \caption[XXX] {
        A moving rectangle is controlled by peers connected indirectly.
        Users can press \code{↑ ↓ → ←} to change the direction of the
        rectangle or \code{SPACE} to pause the application.
        The inputs are applied simultaneously in all peers, as if they were
        mirrors of a single application.
        Video: \url{http://youtube.com/TODO}
        \label{fig.move}
    }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{middleware}
  \caption{
    Applications generate asynchronous events and communicate through an API
    with the middleware.
    The middleware orchestrates the peers, synchronizing their ticks locally
    and broadcasting events with a $\Delta$ delay.
    \label{fig.middleware}
  }
\end{figure}

@@

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{topo}
  \caption{
    \label{fig.topo}
    Network topology: 21 peers organized as a straight line ($0-3$), a simple
    cycle ($3-8$), a second straight line ($8-11$), a full connected cycle
    ($12-17$), and a third straight line ($17-20$).
    %An optional link ($0,20$) creates a long cycle in the network.
  }
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=2in]{mult}
  \caption{
    \label{fig.mult}
Event delays in $ms$ considering the network latency, delay multiplier, and the
average of 5 hops between peers from Figure~\ref{fig.topo}.
    }
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{baks}
  \caption{
    \label{fig.baks}
The $5x$, $2x$, and $x$ delay regions each contains $36$ measures for multiple
configurations of event rate ($5-200~evt/min$ and network latency ($5-500ms$).
%
The color thresholds (\emph{white}, \emph{yellow}, \emph{red}, \emph{black})
are arbitrary but help to distinguish between regions of interest.
%
The experiments uses $1$ process for each peer in a single Linux machine
(\emph{i7/16GB}).
    }
\end{figure*}

@@

\bibliography{p2p-22}
